---
title: "Description?"
---

## Challenges Crash Course

For those who don't watch the show... there are three challenges per episode:

-   "Signature": bakers are given a prompt and requirements ahead of time

-   "Technical": the judges choose a dish that all bakers must attempt to recreate with a pared down recipe. Bakers are scored from 1 (first) to however many bakers.

-   "Showstopper": basically the same as the signature, just at a bigger, more complicated scale

## Description Lengths

Descriptions are provided by the baker. Could a shorter description mean they haven't thought it through or it's not complicated enough? Could longer descriptions *be* more complicated and leave more room for error?

### Signature Challenges

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(bakeoff)

read_rds("sig_desc_length.rds")
```

### Showstopper Challenges

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(bakeoff)

read_rds("show_desc_length.rds")
```
